\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results }

### 2020-06-09 CAOspinaCDGRIN02.tex
Hice los cambios y modificaciones de la celda, los estilo de letra de los pie de imagenas

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\begin{document}

\maketitle
\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
  revista.}
\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
  juntes mis líneas.}
\notaL{Quité paquetes no escenciales}
\notaL{Cuida de no poner espacios al final de las líneas.}

\begin{abstract}
We propose a simple setup which allows the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
\section{Introduction}

\notaL{No entiendo nada de la introducción}
The structural properties of nanostructured materials  has  received a
considerable attention,  and a large research effort has been devoted
to them \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PS the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PS
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory}
\subsection{Calculation of the current density}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the speed of attack and the width of the
porous layer. Nevertheless, it is not a simple to task to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures. Thus, a system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be in principle be numerically calculated for a
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

The effective conductivity of the relatively thin sample in contact
with the grounded counterelectrode is large enough that we may assume its
surface $z=0$ is an equipotential.
On the other hand, no current can go across the insulating walls of
the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson's
equation with a point charge source
  \label{eq:poisson}
  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
with mixed boundary conditions
  \label{eq:ground}
  \varphi(x,y,0)=0,
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
,z)=E_{{_z}}(x, y ,c)=0.
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
$q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
charges. The images include a reflection on the conducting bottom of the
cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
to guarantee that the bottom stays at potential zero.
There are further images on the four walls of the cell, of the same charge $q_0$
and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
them. Similarly, there is an image of the same charge $q_0$ at
$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
surface of the electrolyte. Furthermore, each image charge has to be
further reflected by each of the aforementioned surfaces, yielding new
images.
\begin{figure}
  \includegraphics[width=\textwidth]{paper-1}
  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
    tip of the electrode (red dot) and its images on the walls of the
    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
    $y=0,b$. The relation of some charges and their images is
    indicated by dashed arrows, with a bar to indicate the
    corresponding reflecting wall. The system may be interpreted as a
    periodic lattice with a rectangular unit cell of size $2a\times 2b$,
    one of which is indicated  by wide dashed lines, and with a basis of four equal
    charges at $(\pm x_0, \pm y_0, z_0)$.}
  \label{fig:topview}
In Fig. \ref{fig:topview} we illustrate the real charge and all of
its images within the plane $z=z_0$. They form a periodic rectangular
lattice with a unit cell of size $2a\times 2b$ and with a basis of
four equal charges situated at the positions $\bm r_0$, $\bm
r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
-y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
image charges.
\begin{figure}
  \includegraphics[width=\textwidth]{paper-2}
  \caption{Side view of the electrolytic cell (light blue)
    showing the charge at the tip of the electrode (red dot), its
    images within the plane $z=z_0$ (blue dots), and its images at the
    surface of the sample and the top of the electrolyte (green
    dots). We use solid dots to denote particles with the same charge
    as that corresponding to the tip $q_0$, and open dots for those of
    opposite charge. The system may be interpreted as a periodic
    lattice with a rectangular unit cell of size $2a\times 4c$, one of
    which is indicated by wide dashed lines, and with a basis of four
    charges $q_0$ and another four charges $-q_0$.}
  \label{fig:sideview}
Each plane of charges upon reflection on the surface of the sample yields an
plane of image charges of the opposite sign, while reflections
on the surface of the liquid yields a plane of charges of the same
sign. The side view may be interpreted as a periodic rectangular
lattice with a unit cell of size $2a\times 4c$ containing a basis of eight point
charges, four positive and four negative. A projection onto the $yz$
plane would similarly yield a rectangular lattice with a  $2b\times4c$
unit cell. Putting everything together, the problem is that of solving
Poisson's equation within an orthothombic lattice of size
$2a\times2b\times4c$ with a basis of 16 point charges arranged in
positive and negative planes.

\textbf {Problem considerations}: The problem is the potential, the
field and the current produced by a periodic 2D network of a real load
and all its images. The potential due to a periodic network is
automatically found in the plane making a sum of 2D Fourier.

@@

 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)

@@

Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle
\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.

@@

 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
   (z-z_0)

@@

Solving the homogeneous equation above and below $ z = z_0 $, using
symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
adjusting the singularity

@@

 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)

@@

For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
L_x L_y $ is the unit cell area

@@

 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}

@@

 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}

@@

 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)

@@

\begin{figure}

@@

  \includegraphics[scale=.6]{Images/celd1}
  \caption{\emph{Diagram shows that there is a positive (real) plane $
      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
      $) and its images are a positive plate at $ 2c-z_0 $ and a
      negative plate at $ 2c + z_0 $, the image is repeated vertically
      with the period $ L_z = 4c $}}

@@

In Fig. \ref{fig:Celda1} it is observed that there is a positive
(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
would be rewritten, like this

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
   \vec{r}}\\

@@

The constant K is chosen thus $ \phi (z = 0) $, substituting in
Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
explicitly left with the geometric sum over $n$

@@

    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y

>>>>

\documentclass[12pt,letterpaper,onecolumn,twoside]{article}
\usepackage[spanish]{babel} 
\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}\lhead{}\chead{}\rhead{}
\renewcommand{\headrulewidth}{0pt}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage{subfigure} % subgráfico
\usepackage{lscape}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[noblocks]{authblk}
\usepackage{float}
\usepackage{cite}% para contraer referencias
\usepackage[usenames]{color}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\norm}[1]{\lVert#1\rVert}
 \title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }

\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochan }
\author[3]{V. Agarwal }

\affil[1]{{\scriptsize Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA), Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP 62209, México}}
\affil[2]{{\scriptsize Instituto de Ciencias F\'isica ,Universidad Nacional Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca, Morelos, Mexico  } }
\affil[3]{{\scriptsize Centro de Investigaci\'on en Ingenier\'ia y Ciencias Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  } }
\affil[*]{{\scriptsize Corresponding author: xxxxxx@xxxx.xxx}}
\date{}

\begin{document}
\renewcommand{\contentsname}{Contents}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\tablename}{Table}
\vspace{50pt}

\maketitle
\begin{abstract}
The current density in a of Porous Silicon (PSi) with gradient  refractive index (GRIN) produced  by an electrochemical  attack on silicon (Si)  to  produce  porous  silicon (PSi), the calculated  porosity  of the GRIN structure depends  on the  position  and  distance  from  counter  electrode.   The proposed relationship shows, the  counter  electrode tip that acts  analogously  as a point charge  and  current density  for a geometry in an electrolytic  box by solving the electrostatic equations  with suitable  contour conditions.  Resulting  in an electrostatic model for photonic  crystals  with gradient refractive index (EMPCGRIN). The characterization of the  silicon structures was performed  by scanning electron microscopy   and  UV-Vis-NIR reflectance spectroscopy.  The obtained  results  open  the  possibility  of creating  silicon-based photonic  structures within  the  Visible-IR- range, within  the  sample at  different measuring distances,  where generally porous silicon does not strongly  absorb or disperse light.  Similarly, in the UV-Visible range  there is a strong absorption with more of light scattering. Having a greater  area of attack generating  different pores sizes and their porosity, and making an easy calculation  in the manufacture of porous silicon. \\

Keywords: Porous Silicon (PSi); Monolayer(Ml); Porosity(P); Reflectance Spectra.
\end{abstract}

\vspace{-0.8cm}
\singlespacing 
\tableofcontents

%\newpage
\spacing{1}

 \section{Introduction}

 The structural behavior of nanostructured materials  has  become a  great  topic  of global  interest,  where numerous  research has been done so far \cite{I1}. We found a great way to go for future technological  explorations,  countless  challenges and  that  open a range of possibilities to develop further  study  on these issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured material and an excellent candidate as a technological platform for different sensing applications \cite{I3, I4}, due to its easy manufacturing,  large surface area, high surface reactivity,  and moreover, its optical transduction capacity.  Photonic crystals are multilayer dielectric structures that have periodicity in the dielectric function along one direction \cite{I5}. It has numerous studies for high reflectivity and the ability to adjust  the photonic  prohibited  band (PBG)\cite{I6} , which leads to possible applications  such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the conventional manufacturing of PSi the desired result  is to obtain  homogeneous samples (same structural characteristics) from the  periphery  to the center  of the electrochemically  attacked area.  However, with an asymmetric anodizing configuration,  samples with a lateral gradient in terms of pore size and thickness of the porous layer are obtained \cite{I101}. In this configuration,  the face of the platinum  electrode (cathode)  is relatively maintained  perpendicular  to the surface of the Si substrate (anode) at one end of the cell, so that the distribution of the current within the electrolyte  solution varies depending on the distance  of the electrode due to the resistance of the electrolyte,  resulting  in a decrease in current density as the distance from the electrode increases \cite{I102, I103}. The result is a porous surface with different pore sizes ranging from a few nanometers  to pores on the order of a few micrometers  \cite{I104}. The dimensions of the pores obtained on the same chip can be controlled by adjusting the anodizing current and electrolyte concentration \cite{I11}. Currently, these types of samples have found their application relevant as optical band filters \cite{I12}, devices with a multidirectional photonic band (photonic bar codes) \cite{I13} and mainly as biosensors. In this way, the effect of different topographies (porosities in the same sample) on the culture / adhesion of certain cells \cite{I14} is studied, considerably reducing the number of samples and cost of the study. In addition, they are also very useful when a biomolecule size-exclusion technique is required allowing the identification and separation of these biological compounds \cite{I15}. Recent studies  have shown that  the  combination  of thermal  oxidation  and infiltration of TiO2   by ALD offers the  opportunity to manufacture  a high index of refraction  of contrast, visibly transparent GRIN optical elements from PSi absorbent structures \cite{I16}. A Despite previous research on the formation of porous silicon with GRIN, type p in manufacturing and characterization, there was no control of current densities, much less a model that  explained said lateral  gradient. In this work, we reported a gradient refractive index (GRIN) structure by varying the current density on the fabrication of porous silicon photonic structure. This current density values, depth, and porosity of the photonic structure were calculated from an electrostatic model for photonic crystals with a gradient refractive index (EMPCGRIN). Moreover, the theoretical and experimental studies were exhibited similar results.\\

@@

 \section{Theory}
 \subsection{Electrostatic Model for Photonic Crystals with Gradient Refraction Index (EMPCGRIN)}
The calculate  current density in a GRIN structure produced by an electrochemical attack on Si to produce Porous Si with a position-dependent porosity due to the distance to the counter electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b horizontal and c vertical. Here c considered as the height of the liquid, and the walls are insulating, but the bottom is completely covered with the sample, which act as good conductor. The electrode is a thin insulated cable with tip, which  a point  current source.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.4]{../Images/celdan} 
	\caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $ \sigma $ is the conductivity. This for the stationary case $ \bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived from the electric potential, $\vec {E} = - \bigtriangledown \varphi $.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the sample is a relatively good conductor, when connected to earth $ \varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
  \begin{equation}
\int ds \cdot \vec{E} = \dfrac{I}{\sigma} 	
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
  \begin{equation}
 q_{_{0}} = \dfrac{I}{4 \pi \sigma} 	
 \end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the tip of the electrode that is in the presence of a ground conductor plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0, y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of the liquid is also not conductive to $ (x, y, c) $, the normal current is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E} \cdot \hat{n}=0  $. i.e 
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By using the simplified prism geometry  can solve the problem using the theory of image loads. Each load has an image of the same sign and magnitude for each lateral insulating surface and the opposite sign change in the lower part of the conductive plane, as follows.
 \begin{figure}[H]
 \centering
 \includegraphics[scale=.6]{../Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a real charge in the corner of the cell with its charges ($ q $) images of the same sign in $ Z_0 $ and another charge image ($ -q $) with change of sign located below the conductor in position $ -Z_0 $. b) The upper face seen from above, a real load and its image loads in $ Z_0 $. c) All this formed a systems of a real load and its image loads produced by the cell walls and its other images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $) in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$ due to a reflection in $ (x, 0, z) $ y the image of the image in $\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then, these four charges are reflected on the other two surfaces and the eight new images are reflected on the original surface, etc., producing a periodic 2D rectangular network with unit cells of signs $ L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This entire network is reflected from the bottom with an opposite sign load (below the driver). Periodic copies separated by the vacuum in the $ xy $ plane whose area is being increased to achieve convergence. \\
\textbf {Problem considerations}: The problem is the potential, the field and the current produced by a periodic 2D network of a real load and all its images. The potential due to a periodic network is automatically found in the plane making a sum of 2D Fourier.

@@

 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)

@@

Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal network. It is written $ \phi (\vec{r}) = \displaystyle \sum _ {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.

@@

 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)= -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta (z-z_0)

@@

Solving the homogeneous equation above and below $ z = z_0 $, using symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} = \phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And adjusting the singularity

@@

 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)

@@

For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2 \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A = L_x L_y $ is the unit cell area 	

@@

 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}

@@

 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} ) +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg( e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}

@@

 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)

@@

\begin{figure}[H]

@@

	\includegraphics[scale=.6]{../Images/celd1}
	\caption{\emph{Diagram shows that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $, the image is repeated vertically with the period $ L_z = 4c $}}

@@

In Fig. \ref{fig:Celda1} it is observed that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $. Also, the image is repeated vertically with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11} would be rewritten, like this

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n} -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg) +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg( \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}} +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}  \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\\

@@

The constant K is chosen thus $ \phi (z = 0) $, substituting in Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are explicitly left with the geometric sum over $n$

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0} \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz) \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} - e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
